\begin{summary}
Dear leaders\\
\\
\\
\\
Firstly welcome to attend this international energy summit. As you all considered, our society is now facing a significant problem of energy shortage, especially fuel engery. Thus, the application of new type of energy is of great importance. As for now, the electric energy is the most cutting-edge energy that can be applied to daily life. For instance, the fuel-consuming vehicles can be gradually replaced by the all-electric transportation. However, that requires the efforts of governments to develop a plan to gradually migrate personal transportation towards all- electric cars and we believe that one day electric vehicles will be the major type of transportation.Thus the old vehicles can be banned. In order to further assist the governments to develop their national plans, we offer following suggestions based on our research model:
 Firstly, when making the plan, the geographic, the population density, and the wealth distribution are the three major external factors to consider. These factors decide the possible sites of charging stations.
Secondly, the construction fee, and the local demand are the major internal factors to consider. These factors further decide how to choose the best possible locations of charging stations given a number of possible sites.
In the first a few starting years of developing the plan, gasoline stations are the major sites the governments should focus on. As on the one hand, gasoline stations satisfy all external factors, thus are possible sites for charging stations. On the other hand, According to the past construction plan of charing stations in some countries, gasline stations are suitable sites for charging stations considering their practical experience.
Lastly, fuel-consuming vehicles is a competitive factor to consider comparing to electric vehicles. Based on our model, in the future seven to eight years, the electric transportation will be the major type of personal transportation and the fuel-consuming vehicles will be replaced.

\end{summary}
